---
title: Meldeplattform
name:
date: 2023-02-22
---

# Welcome to Rmarkdown!

Rmarkdown documents are a nice way to combine text with code.

```{r}
print("This is a code chunk.")
```

```{r}
print("Inside this chunk, every character counts!"]
```

Outside the chunk, you're safe! This text will not be executed as code. Feel free to edit and take your own notes here.

You can follow markdown conventions to produce beautiful documents: https://www.markdownguide.org/basic-syntax/

# Load packages

Packages (or libraries, or modules) are pieces of code that can be used in your own code.

We will be relying on two packages today:

```{r}
library(tidyverse)
library(jsonlite)
```

If you get an error while executing this, you will need to install the missing packages first.

# Get data from API

```{r}
url <- ""
response <- read_json(url)
```

# Explore the response

The response is a "nested" list: A list of lists (of lists)...

What entries are in the list?

```{r}
```

Let's explore the entries:

```{r}
```

What is some information that is visible here but not in the browser?

What is visible in the browser but obscured here?

# Convert to tabular format

This next bit is some classic "data wrangling".

```{r}
alerts <- response$features %>%
  map(\(f) { as.list(unlist(f)) }) %>%
  bind_rows()
```

# Get a feeling for the dataset

```{r}
```

# How frequent are the categories?

```{r}
alerts %>%
  ggplot(aes()) +
  geom_
```

# Who reports these things?

```{r}
alerts %>%
  group_by() %>%
  summarize()
```

# What about Kettenhofweg?

```{r}
```

# If we have time: Let's do some mapping!

...
